\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-17 journalWallFriction/simulation.tex
changed order of section on the model, removed one plot
A lot of changes to figures.

 The contour plots in Fig.~\ref{fig:contour} left show the length of the path for two different settings. Top row considers \{$s_1,s_2,g_1$\} = \{$(0.2,0.2),(-0.1,-0.1),(-0.5,0)$\} and middle and bottom row considers  \{$s_1,s_2,g_1$\} = \{$(0.2,0.2),(-0.1,-0.1),(-0.5,0)$\} in a workspace with $r= 0.5$, and $g_2$ ranging over all the workspace. Fig.~\ref{fig:contour} right shows the total distance of the path. This plot shows the nonlinear nature of the path planning. The path length grows when the goals have $\pi$ difference and are very close to the boundary. 
 The worst case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Fig.~\ref{fig:contourPlots} shows the same concepts in a square workspace. Fig.~\ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. All of the discussed plots have considered the particles to be unique. If particles are interchangeable and it does not matter to put the specific particle to its goal location, the path length will be significantly smaller. The bottom row of Fig.~\ref{fig:contour} and Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{numcontour.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{distcontour.pdf}\end{overpic}
 \vspace{-2em}
\caption{\label{fig:contour}
Plots show performance with one goal on the boundary.
}
\end{figure}

\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{deltanum.pdf}\end{overpic}\\
\vspace{1em}
\begin{overpic}[width=\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
The worst case occurs when particles must swap antipodes. This can never be achieved but can be asymptotically approached. Plots show decreasing error as the number of moves grows.
} 
\vspace{-1em}
\end{figure}

>>>>

 The contour plots in Fig.~\ref{fig:contour} left show the length of the path for two different settings. Top row considers \{$s_1,s_2,g_1$\} = \{$(0.2,0.2),(-0.1,-0.1),(-0.5,0)$\} and middle and bottom row considers  \{$s_1,s_2,g_1$\} = \{$(0.2,0.2),(-0.1,-0.1),(-0.5,0)$\} in a workspace with $r= 0.5$, and $g_2$ ranging over all the workspace. Fig.~\ref{fig:contour} right shows the total distance of the path. This plot shows the nonlinear nature of the path planning. The path length grows when the goals have $\pi$ difference and are very close to the boundary. 
 The worst case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Fig.~\ref{fig:contourPlots} shows the same concepts in a square workspace. Fig.~\ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. All of the discussed plots have considered the particles to be unique. If particles are interchangeable and it does not matter to put the specific particle to its goal location, the path length will be significantly smaller. The bottom row of  Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles.

@@

\begin{figure}
\centering
\begin{overpic}[width=0.49\columnwidth]{worstnum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{worstdist.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{middlegoalnum.pdf}\end{overpic}
\begin{overpic}[width=0.49\columnwidth]{middlegoaldist.pdf}\end{overpic}
\caption{\label{fig:contour}
Plots show performance with one goal on the boundary.
}
\end{figure}

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{deltanum.pdf}\end{overpic}\\
%\vspace{1em}
\begin{overpic}[width=\columnwidth]{deltadist.pdf}\end{overpic}
\caption{\label{fig:deltanumdist}
The worst case occurs when particles must swap antipodes. This can never be achieved but can be asymptotically approached. Plot shows decreasing error as the number of moves grows.
} 
\vspace{-1em}
\end{figure}
